% The Computer Society usually requires 10pt for submissions.

\documentclass[a4paper,14pt]{article}
\usepackage{geometry}
\usepackage[colorlinks, linkcolor=blue]{hyperref}
\begin{document}


\title{Global Contrast based Salient Region Detection 
    \footnote{Project page:
    \href{http://cg.cs.tsinghua.edu.cn/people/\~cmm/saliency/}
    {http://cg.cs.tsinghua.edu.cn/people/$\sim$cmm/saliency/}} 
}

\author{\small Ming-Ming Cheng$^{1}$\quad Guo-Xin Zhang$^{1}$ \quad Niloy J. Mitra$^{2}$
    \quad Xiaolei Huang$^{3}$  \quad Shi-Min Hu$^{1}$  \\
    $^{1}$ TNList, Tsinghua University \quad \quad
    $^2$ KAUST   \quad \quad $^3$ Lehigh University\\
    {\tt \small chengmingvictor@gmail.com}
}

\date{}
\maketitle

\begin{abstract}
Reliable estimation of visual saliency allows appropriate processing of images without prior
knowledge of their contents, and thus remains an important step in many computer vision tasks
including image segmentation, object recognition, and adaptive compression.
We propose a regional contrast based saliency extraction algorithm,
which simultaneously evaluates global contrast differences and spatial coherence.
The proposed algorithm is simple, efficient, and yields full resolution saliency maps.
Our algorithm consistently outperformed existing saliency detection methods, yielding
higher precision and better recall rates, when evaluated using one of the largest
publicly available data sets.
We also demonstrate how the extracted saliency map can be used to create high quality
segmentation masks for subsequent image processing.
\end{abstract}


\textbf{Keywords:}\quad
Saliency detection, global contrast, early and biologically-inspired Vision.



\vspace{.1in}

\paragraph{Disclaimer: }
The documents contained in these pages are included to ensure timely
dissemination of scholarly and technical work on a non-commercial basis.
Copyright and all rights therein are maintained by the authors or by other
copyright holders, notwithstanding that they have offered their works here
electronically. It is understood that all persons copying this information
will adhere to the terms and constraints invoked by each author's copyright.
These works may not be reposted without the explicit permission of the
copyright holder.

\vspace{.2in}

{\footnotesize % "\tiny", "\scriptsize", "\footnotesize", "\small", "\normalsize", "\large", "\Large", "\LARGE", "\huge", "\Huge"
\begin{verbatim}
@conference{11cvpr/Cheng_Saliency,
  title={Global Contrast based Salient Region Detection},
  author={Ming-Ming Cheng and Guo-Xin Zhang and Niloy J. Mitra and Xiaolei Huang and Shi-Min Hu},
  booktitle={IEEE CVPR},
  pages={409--416},
  year={2011},
}
\end{verbatim}
}

\end{document}


